\item \textbf{Kim, Chang-Goo}; Ostriker, Eve C.; Kim, Jeong-Gyu; Gong, Munan~\textit{et al.}, \textit{Metallicity Dependence of Pressure-Regulated Feedback-Modulated Star Formation in the TIGRESS-NCR Simulation Suite}, 2024 (\arxiv{2405.19227}), ApJ in press

\item \student{Guo, Minghao}; Stone, James M.; Quataert, Eliot; \textbf{Kim, Chang-Goo}, \textit{Magnetized Accretion onto and Feedback from Supermassive Black Holes in Elliptical Galaxies}, 2024 (\arxiv{2405.11711}) [\href{http://adsabs.harvard.edu/abs/2024arXiv240511711G}{2 citations}], ApJ in press

\item Pingel, N. M.~\textit{et al.}~(incl. \textbf{CGK}), \textit{The Local Group L-Band Survey: The First Measurements of Localized Cold Neutral Medium Properties in the Low-Metallicity Dwarf Galaxy NGC 6822}, 2024 (\arxiv{2407.13829}), ApJ in press

\item Steinwandel, U. P.~\textit{et al.}~(incl. \textbf{CGK}), \textit{Pumping Iron: How turbulent metal diffusion impacts multiphase galactic outflows}, 2024 (\arxiv{2407.14599}), ApJ submitted

\item Diesing, Rebecca; Guo, Minghao; \textbf{Kim, Chang-Goo}; Stone, James~\textit{et al.}, \textit{Nonthermal Signatures of Radiative Supernova Remnants}, 2024 (\arxiv{2404.15396}), ApJ submitted

\item Sarbadhicary, S. K.~\textit{et al.}~(incl. \textbf{CGK}), \textit{Where do stars explode in the ISM? -- The distribution of dense gas around massive stars and supernova remnants in M33}, 2023 (\arxiv{2310.17694}) [\href{http://adsabs.harvard.edu/abs/2023arXiv231017694S}{4 citations}], ApJ submitted